Leaf traits drive differences in biomass partitioning among major plant functional types

### 2014-12-16 manuscript.Rnw
Added a couple of notes, two tables next to each other for comparison

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage[default,osfigures,scale=0.95]{opensans}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\usepackage{authblk}
\usepackage{gensymb}
\usepackage{longtable}
\usepackage{lineno}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\bibliographystyle{plain}

@@

@@

\item It is also unclear whether PFTs with higher leaf biomass will have higher total leaf area, because PFTs differ in the ratio of leaf mass to area (LMA), a measure of the leaf construction cost. Leaf area itself is relevant because light interception acts on leaf area, which drives photosynthesis. A few classic studies have assumed that gymnosperms indeed carry much more leaf area than angiosperms (Chabot Hicks, plus another). 

@@

\item Regardless of how we analyzed it, we found only weak climate effects. We did not find differences between biomes in $M_F/A_S$ (Fig 3), but some small inconsistent differences in $A_F/A_S$ (corresponding to slightly lower LMA in tropical vs. temperate evergreen angiosperms). Biome consistently explained very little variation when added to a statistical model in addition to PFT and plant height (Table S7 SHOULD BE IN MAIN TEXT). 

>>>>

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage[default,osfigures,scale=0.95]{opensans}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\usepackage{authblk}
\usepackage{gensymb}
\usepackage{longtable}
\usepackage{lineno}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}

\bibliographystyle{plain}

@@

\item It is our intent to evaluate and critique alternative models of biomass allocation (wbe etc), but rather to establish, empirically, patterns in biomass partitioning across plant functional types and plant size.

@@

\item Novelty in this study, a) individual plants, b) entire size range including saplings and the largest trees in the world, c) estimates of leaf area as well as mass d) further division into three plant functional types, and three biomes
\item It is unclear whether PFTs with higher leaf biomass will have higher total leaf area, because PFTs differ in the ratio of leaf mass to area (LMA), a measure of the leaf construction cost. Leaf area itself is relevant because light interception acts on leaf area, which drives photosynthesis. A few classic studies have assumed that gymnosperms indeed carry much more leaf area than angiosperms (Bond; Chabot and Hicks). 

@@

\item Regardless of how we analyzed it, we found only weak climate effects. We did not find differences between biomes in $M_F/A_S$ (Fig 3), but some small inconsistent differences in $A_F/A_S$ (corresponding to slightly lower LMA in tropical vs. temperate evergreen angiosperms). Biome consistently explained very little variation when added to a statistical model in addition to PFT and plant height (Table S6). 
